### 2016-07-18 paper/algorithms.tex
Added online-offline algorithm

>>>>

Algorithm~\cref{alg:refSeries} can be naturally extended to an online-offline setting, where a multi-fidelity model adaptive constraint can be generated for a given data set in the offline phase. In the online phase, additional data points are added to the data set, and instead of solving the complete inverse problem with all the data points, and the high-fidelity constraints, an iterative algorithm can be initiated using the multi-fidelity representation developed in the offline phase. The adaptive procedure, with the supplementary adjoint can be used to adapt the preexisting multi-fidelity representation to the new data points.  
%
\alglanguage{pseudocode}
\begin{algorithm}[h!]
\small
\caption{An algorithm to adapt a pre-computed mixed-fidelity model to new data.}
\label{alg:refonoff}
\begin{algorithmic}[1]
\State{Define maximum acceptable absolute relative QoI error \texttt{errTol}}
\State{Given a data set $d_1 \in \R^{n_{d_1}}$, and an adaptively build a mixed-fidelity model for low error in the QoI, use Algorithm~\ref{} to build a MF model MF$_1$} 
\Procedure{$\texttt{Online}$}{HF model, MF model MF$_1$, \texttt{errTol}, $d_2 \in \R^{n_{d_2}}$}
	\State{$i\gets1$}
	\State{Solve for stationary point $\Psi_{MF_1}$ of augmented Lagrangian $\mathcal{M}_{MF_1}$ formed using new data set $d_2$}
	\State{Solve QoI error adjoint equation, linearized about $\Psi_{MF_1}$, for \par\hskip\algorithmicindent supplementary adjoint $\Lambda_1$ (see \cref{eq:superAdjEq})}
	\State{Compute QoI error estimate

	$\epsilon_0=-\frac{1}{2}\mathcal{M}'_{HF,\Psi}(\Psi_{MF_1})(\Lambda_1)+\mathcal M_{HF}(\Psi_{MF_1})-\mathcal M_{MF_1}(\Psi_{MF_1})$}
	\State{Calculate QoI $I(q_{MF_1},u_{MF_1})$}
	\While{$i<$ \texttt{maxIter} and $|\epsilon_i/I(q_{MF_i},u_{MF_i})|>$ \texttt{errTol}}
		\State{\begin{varwidth}[t]{\linewidth}Localize $\epsilon_i$ (see section~\cref{sect:error_est_localize}) and use this decomposition to guide \par\hskip\algorithmicindent formation of new mixed-fidelity model MF$_{i+1}$\end{varwidth}}
		\State{$i\gets i+1$}
		\State{Solve for stationary point $\Psi_{MF_i}$ of augmented Lagrangian $\mathcal{M}_{MF_i}$}
		\State{Solve QoI error adjoint equation, linearized about $\Psi_{MF_i}$, for

		$\quad\quad \epsilon_i=-\frac{1}{2}\mathcal{M}'_{HF,\Psi}(\Psi_{MF_i})(\Lambda_i)+\mathcal M_{HF}(\Psi_{MF_i})-\mathcal M_{MF_i}(\Psi_{MF_i})$}
		\State{Calculate QoI $I(q_{MF_i},u_{MF_i})$}
	\EndWhile \\
\Return{QoI estimate $I(q_{MF_i},u_{MF_i})$ for the new data set $d_2$}
\EndProcedure
\Statex
\end{algorithmic}
\end{algorithm}
%
Algorithm~\cref{alg:refonoff} lends itself to a quasi-incremental data assimilation approach, where the data set $d_2$ is an augmentation of the original set $d_1$. In such a situation, we expect that the model refinement will be concentrated around the new data points, that also inform the QoI. Thus, in the online phase, even though the inverse problem will be solved with all data points, the use of high-fidelity models will be limited, and the bulk of the computation (computing the auxilary variables, and supplementary adjoint) will be focused on identifying those new data points, which have the maximum impact on the QoI.
